### 2019-12-10 Statistical Methods/03_graphical-summaries.rmd
statistical methods, ch3
statistical methods, ch3

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Numerical Summaries}
   \rfoot{\color{headergrey}\thepage}
   \lfoot{\color{headergrey}Chapter 2}
   \fancyfoot[C]{\rmfamily\color{headergrey}Statistical Methods}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

@@

#### Chapter 2

### 2.1

Suppose,

$X_1 = 1, X_2 = 3, X_3 = 0,$
$X_4 = -2, X_5 = 4, X_6 = -1,$
$X_7 = 5, X_8 = 2, X_9 = 10.$

```{r, echo = T}
x <- c(1, 3, 0, -2, 4, -1, 5, 2, 10)
```

Find:

a.) $\sum{X_i}$

```{r, echo = T}
sum(x)
```

b.) $\sum^5_{i=3}X_i$

```{r, echo = T}
sum( x[3:5] )
```

c.) $\sum^4_{i=1}X^3_i$

```{r, echo = T}
sum(x[1:4]^3)
```

d.) $(\sum{X_i})^2$

```{r, echo = T}
(sum(x))^2
```

e.) $\sum{3}$

```{r, echo = T}
3 * length(x)
```

f.) $\sum{(X_i - 7)}$

```{r, echo = T}
sum(x - 7)
```

g.) $3\sum^5_{i=1}X_i - \sum^9_{i=6}X_i$

```{r, echo = T}
3 * sum( x[1:5] ) - sum( x[6:9] )
```

h.) $\sum{10X}$

```{r, echo = T}
sum( 10 * x)
```

i.) $\sum^6_{i=2}iX_i$

```{r, echo = T}
i <- 2:6
sum( i * x[i]  )
```

j.) $\sum6$

```{r, echo = T}
6 * length(x)
```

### 2.2

Express the following in summation notation.

a.) $X_1 + \frac{X_2}{2} + \frac{X_3}{3} + \frac{X_4}{4}$

$\ldots = \frac{X_1}{1} + \frac{X_2}{2} + \frac{X_3}{3} + \frac{X_4}{4}$

$\ldots = \sum{^4}_{i=1}{\frac{X_i}{i}}$

b.) $U_1 + U^2_2 + U^3_3 + U^4_4$

$\ldots = U^1_1 + U^2_2 + U^3_3 + U^4_4$

$\ldots = \sum^4_{i=1}{U^i_i}$

c.) $(Y_1 + Y_2 + Y_3)^4$

$(\sum^3_{i=1}{Y_i})^4$

### 2.3

Show by numerical example that $\sum{X^2_i}$ is not necessarily equal to $(\sum{X_i}^2)$.

```{r, echo = T}
x <- 1:10

sum(x^2)

(sum(x))^2
```

### 2.4

Find the mean and median of the following sets of numbers.

a.) -1, 0, 3, 0, 2, -5.

```{r, echo = T}
x <- c(-1, 0, 3, 0, 2, -5)

mean(x)
median(x)
```

b.) 2, 2, 3, 10, 100, 1,000

```{r, echo = T}
x <- c(2, 2, 3, 10, 100, 1000)

mean(x)
median(x)
```

### 2.5

The final exam scores for 15 students are: 73, 74, 92, 98, 100, 72, 74, 85, 76, 94, 89, 73, 76, 99.

Compute the mean, 20% trimmed mean, and median using R.

```{r, echo = T}
scores <- c(73, 74, 92, 98, 100, 72, 74, 85, 76, 94, 89, 73, 76, 99)

mean(scores)
mean(scores, trim = .2)
median(scores)
```

### 2.6

The average of 23 numbers is 14.7. What is the sum of these numbers?

```{r, echo = T}
23 * 14.7
```

### 2.7

Consider the 10 values: 3, 6, 8, 12, 23, 26, 37, 42, 49, 63.

The mean is $\bar{X} = 26.9$

```{r, echo = T}
x <- c(3, 6, 8, 12, 23, 26, 37, 42, 49, 63)
mean(x)
```

a.) What is the value of the mean if the largest value, 63, is increased to 100?

```{r, echo=T}
x <- c(3, 6, 8, 12, 23, 26, 37, 42, 49, 100)
mean(x)
```

b.) What is the mean if 633 is increased to 1,000?

```{r, echo=T}
x <- c(3, 6, 8, 12, 23, 26, 37, 42, 49, 1000)
mean(x)
```

c.) What do these results illustrate about the mean?

_The mean is very sensitive to outliers._

### 2.8

Repeat the previous exercise, only compute the median instead.

```{r, echo=T}
x <- c(3, 6, 8, 12, 23, 26, 37, 42, 49, 100)
median(x)
```

b.) What is the mean if 633 is increased to 1,000?

```{r, echo=T}
x <- c(3, 6, 8, 12, 23, 26, 37, 42, 49, 1000)
median(x)
```

### 2.9

In general, how many values must be altered to make the sample mean arbitrarily large?

_One._

### 2.10

What is the minimum number of values that must be altered to make the 20% trimmed mean and sample median arbitrarily large?

mean = $g = (.2N), g + 1$

median = ~$.5N$

### 2.11

For the values 0, 23, -1, 12, -10, -7, 1, -19, -6, 12, 1, -3 compute the lower and upper quartiles using the ideal fourths.

```{r, echo = T}
# Used in 11 & 12
idealf <- function( x ) {
   n <- length(x)
   sorted <- sort(x)
   i <- (n / 4) + 5/12
   j <- floor(i)
   h <- i - j
   q1 <- (1 - h)*sorted[j] + h*sorted[j + 1]

   k <- n - j + 1
   q2 <- (1 - h)*sorted[k] + h*sorted[k - 1]

   c(x[1], q1, q2, sorted[n])
}

@@

```{r, echo = T}
x <- c(0, 23, -1, 12, -10, -7, 1, -19, -6, 12, 1, -3)

idealf(x)
```

### 2.12

For the values: -1, -10, 2, 2, -7, -2, 3, 3, -6, 12, -1, -12, -6, 8, 6 compute the lower and upper quartiles (the ideal fourths).

```{r, echo = T}
x <- c(-1, -10, 2, 2, -7, -2, 3, 3, -6, 12, -1, -12, -6, 8, 6)

idealf(x)
```

### 2.13

Approximately how many values must be altered to make _q2_, the estimate of the upper quartile based on the ideal fourths, arbitrarily large?

_About $\frac{1}{4}$_

### 2.14

Argue that the smallest observed value, $X_1$, satisfies the definition of a measure of location.

_The smallest (or largest) value in a set defines the boundaries of the set. This is by definition a measure of location._

### 2.15

The height of 10 plants is measured in inches and found to be 12, 6, 15, 3, 12, 6, 21, 15, 18 and 12.

```{r, echo = T}

x <- c(12, 6, 15, 3, 12, 6, 21, 15, 18, 12)

xbar <- mean(x)

stopifnot( sum( x - xbar ) == 0 )

@@

Verify that $\sum(X_i - \bar{X}) = 0$

### 2.16

For the data in the previous exercise, compute the range, variance and standard deviation.

```{r, echo = T}

@@

range <- max(x) - min(x)
variance <- (1/(n-1))*sum( ( x - xbar )^2)
stdDev <- sqrt(variance)

@@

$\bar{X} = `r xbar`$, Range = `r range`, $Var = `r variance`$, $\sigma = `r stdDev`$

\newpage

### 2.17

Use the rules of summation notation to show that it is always the case that $\sum(X_i - \bar{X}) = 0$.

$\bar{X} = \frac{1}{n}\sum{X_i}$

$\sum{X_i} - \frac{1}{n}\sum{X_i}$

$\ldots = \frac{1}{n}\sum{X_i} - \sum{X_i}$

$\ldots = \frac{1}{n}(\sum{X_i - X_i})$

$\ldots = \frac{1}{n}(0)$

$\ldots = 0$

### 2.18

Seven different thermometers were used to measure the temperature of a substance. The reading in degrees Celsius are -4.10, -4.13, -5.09, -4.08, -4.10, -4.09 and -4.12.

```{r, echo = T}
x <- c(-4.10, -4.13, -5.09, -4.08, -4.10, -4.09, -4.12)
n <- length(x)
xbar <- 1/n*sum(x)
variance <- (1/(n-1))*sum( (x - xbar)^2 )
stdDev <- sqrt(variance)
```

Find the variance and standard deviation.

$Var = `r variance`$, $\sigma = `r stdDev`$

### 2.19

A weightlifter's maximum bench press (in pounds) in each of 6 successive weaks was 280, 295, 275, 305, 300, 290.

Find the standard deviation.

```{r, echo = T}
x <- c(280, 295, 275, 305, 300, 290)
n <- length(x)
xbar <- 1/n*(sum(x))
variance <- (1/(n-1))*sum( (x - xbar)^2)
sqrt(variance)
```

### 2.20

For the values,

20, 121, 132, 123, 145, 151, 119, 133, 134, 130, 200

use the classic outlier detection rule to determine whether any outliers exist.

```{r, echo = T}
x <- c(20, 121, 132, 123, 145, 151, 119, 133, 134, 130, 200)

x[ abs(x - mean(x)) / sd(x) > 2 ]

@@

### 2.21

Apply the boxplot rule and the MAD-median rule using the values in the preceding exercise. Note that the results differ, compared to using the classic rule.

```{r, echo = T}

x[ abs( x - median(x) ) / mad(x) > 2.27 ]

Explain why this happened.

_The classic method masks the value 200 as an outlier._

### 2.22

Consider the values,

0, 121, 132, 123, 145, 151, 119, 133, 134, 130, 250.

```{r, echo = T}
x <- c(0, 121, 132, 123, 145, 151, 119, 133, 134, 130, 250)

x[ ( abs(x - mean(x)) /sd(x) ) > 2 ]

Are the values 0 and 250 declared outliers using the classic outlier detection rule?

_Yes._

### 2.23

Verify that for the data in the previous exercise, the boxplot rule declares the values 0 and 250 outliers.

```{r, echo = T}

bounds <- quantile(x)[c(2,4)]

lower <- bounds[1] - 1.5*(bounds[2] - bounds[1])
upper <- bounds[2] + 1.5*(bounds[2] - bounds[1])

x[ x < lower | x > upper]

### 2.24

Consider the values

20, 121, 132, 123, 145, 151, 119, 133, 134, 240, 250

Verify that no outliers are found using the classic outlier detection rule.

```{r, echo = T}
x <- c(20, 121, 132, 123, 145, 151, 119, 133, 134, 240, 250)

stopifnot( length( x[ ( abs( x - mean(x) ) / sd(x) ) > 2] ) == 0 )

### 2.25

Verify that for the data in the previous exercise, the boxplot rule declares the values 20, 240 and 250 outliers.

```{r, echo = T}
x <- c(20, 121, 132, 123, 145, 151, 119, 133, 134, 240, 250)

bounds <- quantile(x)[c(2,4)]

lower <- bounds[1] - 1.5*(bounds[2] - bounds[1])
upper <- bounds[2] + 1.5*(bounds[2] - bounds[1])

x[ x < lower | x > upper]

### 2.26

What do the last three exercises suggest about the boxplot rule versus the classic rule for detecting outliers?

_The classic boxplot rule masks outliers._

### 2.27

What is the typical pulse rate (beats per minute) among adults? Imagine that you sample 21 adults, measure their pulse rate, and get:

80, 85, 81, 75, 77, 79, 74, 86, 79, 55, 82, 89, 73, 79, 83, 82, 88, 79, 77, 81, 82

```{r, echo = T}
x <- c(80, 85, 81, 75, 77, 79, 74, 86, 79, 55, 82, 89, 73, 79, 83, 82, 88, 79, 77, 81, 82)
```

compute the 20% trimmed mean.

```{r, echo = T}

n <- length(x)
o <- sort(x)
g <- floor(.2*n)
t <- o[ (g+1):(n-g) ]
tbar <- 1/(n - 2*g)*sum(t)

stopifnot(tbar == mean(x, trim = .2))
```

### 2.28

For the observations,

21, 36, 42, 24, 25, 36, 35, 49, 32

```{r, echo = T}
x <- c(21, 36, 42, 24, 25, 36, 35, 49, 32)
n <- length(x)

xbar <- 1/n * sum(x)

o <- sort(x)
g <- floor(.2*n)
t <- o[ (g+1):(n-g) ]
tbar <- 1/(n - 2*g)*sum(t)

M <- o[ (n + 1)/2 ]

Verify that the sample mean, 20% trimmed mean, and median are $\bar{X} = 33.33, \bar{X}_t = 32.9, and \ M = 35$

$\bar{X} = `r xbar`$, $\bar{X}_t = `r tbar`$, $M = `r M`$

### 2.29

The largest observation in the last problem is 49. If 49 is replaced by the value 200, verify that the sample mean is now $\bar{X} = 50.1$ but the 20% trimmed mean and median are not changed.

```{r, echo = T}
x <- c(21, 36, 42, 24, 25, 36, 35, 200, 32)

xbar <- 1/n * sum(x)

o <- sort(x)
g <- floor(.2*n)
t <- o[ (g+1):(n-g) ]
tbar <- 1/(n - 2*g)*sum(t)

M <- o[ (n + 1)/2 ]
```

$\bar{X} = `r xbar`$, $\bar{X}_t = `r tbar`$, $M = `r M`$

### 2.30

For the data in Exercise 28, what is the minimum number of observations that must be altered so that the 20% trimmed mean is greather than 1,000?

$g + 1 = `r g + 1`$

### 2.31

Repeat the previous exercise, but use the median instead.

_N = 4_

What does this illustrate about the resistance of the mean, median and 20% trimmed mean?

_The mean has the least resistance, followed by the trimmed mean and then the median._

### 2.32

For the observations,

6, 3, 2, 7, 6, 5, 8, 9, 11

Use R to verify that the sample mean, 20% trimmed mean, and median are $\bar{X} = 6.5, \bar{X}_t = 6.7 \ and \ M = 6.5$, respectfully.

```{r, echo = T}
x <- c(6, 3, 2, 7, 6, 5, 8, 9, 8, 11)

mean(x)

mean(x, trim = .2)

median(x)
```

### 2.33

In general, when you have _n_ observations, what is the minimum number of values that must be altered to make the 20% trimmed mean grow as larage as you want?

floor(n*.2) + 1

### 2.34

A class of fourth graders was asked to bring a pumpkin to school. Each of the 29 students counted the number of seeds in their pumpkin, and the results were:

250, 220, 281, 247, 230, 209, 240, 160, 370, 274, 210, 204, 243, 251, 190,
200, 130, 150, 177, 475, 221, 350, 224, 163, 272, 236, 200, 171, 98

Use R to compute the sample mean, 20% trimmed mean, median and MOM.

```{r, echo = T}
x <- c(250, 220, 281, 247, 230, 209, 240, 160, 370, 274, 210, 204, 243, 251, 190, 
       200, 130, 150, 177, 475, 221, 350, 224, 163, 272, 236, 200, 171, 98)

xbar <- mean(x)
tbar <- mean(x, trim = .2)
M <- median(x)
MOM <-  mean( x[ abs( x - median(x) ) / mad(x) < 2.27 ] )

$\bar{X} = `r xbar`$, $\bar{X}_t = `r tbar`$, $M = `r M`$, $MOM = `r MOM`$

### 2.35

Compute the 20% Winsorized values for the observations:

21, 36, 42, 24, 25, 36, 35, 49, 32

```{r, echo = T}
x <- c(21, 36, 42, 24, 25, 36, 35, 49, 32)

winsorize <- function( x, trim = .2) {
   n <- length(x)

   o <- sort(x)
   g <- floor(trim*n)

   o[1:(g+1)] <- o[(g+1)]
   o[(n-g):n] <- o[n-g]

   o
}

winsorize(x)
```

### 2.36

For the observations in the pervious problem, use R to verify that the 20% Winsorized variance is 51.36.

```{r, echo = T}

Wvar <- var(winsorize(x))

$W_{var} = `r Wvar`$

### 2.37

In the previous problem, would you expect the sample variance to be larger or smaller than 51.36?

_Larger, Winsorizing pulls in the extremes._

Verify your answer.

```{r, echo = T}
var(x)
```

### 2.38

In general, will the Winsorized sample variance, $s^2_w$, be less than the sample variance, $s^2$?

_Yes._

### 2.39

For the observations,

6, 3, 2, 7, 6, 5, 8, 9, 8, 11

verify that the sample variance and 20% Winsorized variance are 7.4 and 1.8, respectfully.

```{r, echo = T}
x <- c(6, 3, 2, 7, 6, 5, 8, 9, 8, 11)

variance <- var(x)

$Var = `r variance`$, $Var_w = `r Wvar`$

### 2.40

Consider again the number of pumpkin seeds given in Exercise 34.

Compute the 20% Winsorized variance.

```{r, echo = T}
x <- c(250, 220, 281, 247, 230, 209, 240, 160, 370, 274, 210, 204, 243, 251, 190, 
       200, 130, 150, 177, 475, 221, 350, 224, 163, 272, 236, 200, 171, 98)

Wvar <- var( winsorize(x) )

$W_{var} = `r Wvar`$

### 2.41

Snedecor and Cochran (1967) report results from an experiment dealing with weight gaim in rats as a function of source and amount of protein.

One of the groups was fed beef with a low amount of protein. The weight gains were:

90, 76, 90, 64, 86, 51, 72, 90, 95, 78

Compute the 20% trimmed mean and 20% Winsorized variance.

```{r, echo = T}
x <- c(90, 76, 90, 64, 86, 51, 72, 90, 95, 78)

tbar <- mean(x, trim = .2)
wvar <- var(winsorize(x))

$\bar{X}_t = `r tbar`$, $Var_w = `r wvar`$

>>>>

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Graphical Summaries}
   \rfoot{\color{headergrey}\thepage}
   \lfoot{\color{headergrey}Chapter 3}
   \fancyfoot[C]{\rmfamily\color{headergrey}Statistical Methods}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

@@

#### Chapter 3

### 3.1

Based upon a sample of 100 individuals, the values 1, 2, 3, 4, 5 are observed with relative frequencies 0.2, 0.3, 0.1, 0.25, 0.15, respectfully.

Compute the mean, variance and standard deviation.

```{r, echo = T}
values <- c(1, 2, 3, 4, 5)
frequencies <- c(0.2, 0.3, 0.1, 0.25, 0.15)

stopifnot(sum(frequencies) == 1)

n <- 100

xbar <- sum(values * frequencies)
variance <- n/(n - 1) * sum( ((values - xbar)^2) * frequencies )
stdDev <- sqrt(variance)

@@

$\bar{X} = `r xbar`$, $Var = `r variance`$, $\sigma = `r stdDev`$

### 3.2

Fifty individual are rated on how open-mided they are. The ratings have the values 1, 2, 3, 4, and the corresponding relative frequencies are 0.2, 0.24, 0.4, 0.16, respectively.

Compute the mean, variance and standard deviation.

```{r, echo = T}
```

### 3.3

For the values 0, 1, 2, 3, 4, 5, 6, the corresponding relative frequencies based on a sample of 10,000 observations are 0.015625, 0.093750, 0.234375, 0.312500, 0.234375, 0.312500, 0.234375, 0.093750, 0.015625, respectively.

Determine the mean, variance and standard deviation.

```{r, echo = T}
```

### 3.4

For a local charity, the donations in dollars recieved during the last month were 5, 10, 15, 20, 25, 50, having the frequencies 20, 30, 10, 40, 50, 5, respectively.

Compute the mean, variance and standard deviation.

### 3.5

The values 1, 5, 10, 20 have the frequencies 10, 20, 40, 30.

Compute the mean, variance and standard deviation.

### 3.6

For the data in Table 2.1, dealing with changes in cholesterol levels, create a histogram with the R function hist.

```{r, echo = T}
data <- read.csv(paste0(data.dir, "ibtable2_1_dat.txt"), header = F)

@@

### 3.7

For the data in Table 2.2, create a histogram using the R function _hist_ and speculate about whether values less than zero are outliers.

```{r, echo = T}
data <- read.csv(paste0(data.dir, "ibtable2_2_dat.txt"), header = F)

Then compare your answer to the result obtained using _outbox_.

### 3.8

The heights of 30 male Egyptian skulls from 4,000 BC are reported by Thomson and Randall-Maciver (1905) to be:

121, 124, 129, 130, 130, 131, 131, 132, 132, 132, 133, 133, 134, 134, 134,
134, 135, 136, 136, 136, 136, 137, 137, 138, 138, 138, 140, 143.

```{r, echo = T}
x <- c(121, 124, 129, 129, 130, 130, 131, 131, 132, 132, 132, 133, 133, 134, 134, 134,
134, 135, 136, 136, 136, 136, 136, 137, 137, 138, 138, 138, 140, 143)

@@

stopifnot(n == 30)

@@

Create a histogram.

Find outliers with classic rule and MAD-median rule.

### 3.9

For the dta in the previous exercise, verify that the classic outlier detection rule, given by _2.6_, finds three outliers, which match the values flagged as outliers by the MAD-median rule.

Despite this result, what are the concerns with the classic outlier detection rule?

### 3.10

What do Exercises 6 and 7 suggest about using a histogram to detect outliers?

### 3.11

Table 3.5 shows the exam scores for 27 students.

Create a stem-and-leaf display.

### 3.12

If the leaf is the hundredths digit, what is the stem for the number 34.679?

### 3.13

Consider the values 5.134, 5.532, 5.869, 5.809, 5.268, 5.495, 5.142, 5.483, 
5.329, 5.149, 5.240, 5.823.

If the leaf is taken to be the tenths digit, why would this make an uninteresting stem-and-leaf display?

```{r, echo = T}
x <- c(5.134, 5.532, 5.869, 5.809, 5.268, 5.495, 5.142, 5.483, 
5.329, 5.149, 5.240, 5.823)

@@

### 3.14

For the boxplot in Figure _3.11_, determine approximately, the quartiles, the interquartile range, and the median.

Approximately how large is the largest value not declared an outlier?

### 3.15

In Figure _3.11_, about how large must a value be to be declared an outlier? How small?

### 3.16

Use R to create both a boxplot and a plot of the relative frequencies using the film data in Table 3.1.

### 3.17

Use R to create a boxplot and a kernel density estimate using the data in table 3.2.

### 3.18

Describe a situation where the sample histogram is likely to give a good indication of the population histogram based on 100 observations.

### 3.19

Comment generally on how large of a sample size is needed to ensure that the sample histogram will likely provide a good indication of the population histogram?

### 3.20

When trying to detect outliers, discuss the relative merits of using a histogram vs a boxplot.

### 3.21

A sample histogram indicates that the data are highly skewed to the right.

Is this a reliable indication that if all individuals of interest could be measured, the resulting histogram would also be highly skewed?
